\textsf{Are large language models superhuman chemists?}

### 2024-10-18 src/tex/ms.tex
update text

@@

\subsection{Model evaluation workflow}
EXPAND THIS section.

@@

\paragraph{Parsing}
Our parsing workflow is multistep and primarily based on regular expressions.
In the case of instruction-tuned models, we first identify the \texttt{[ANSWER]}\texttt{[\textbackslash ANSWER]} environment we prompt the model to report the answer in.
In the case of completion models, this step is skipped. From there, we attempt to extract the relevant enumeration letters (for multiple-choice questions) or numbers.
In the case of numbers, our regular expression was engineered to deal with various forms of scientific notation.
As initial tests indicated that models sometimes return integers in the form of words, e.g., \enquote{one} instead of \enquote{1}, we also implemented a word-to-number conversion using regular expressions.
If these hard-coded parsing steps fail, we use a \gls{llm}, e.g., Claude 2, to parse the completion.

\paragraph{Models}
Rewrite - as table. The table can then also contain if it has been completion or instruction-prompted.

@@

\paragraph{Comparison with models}
%To compare the performance of humans (who might have answered only some questions) with the performance of models (which answered all questions), we focussed on questions that at least four humans answered and limited the pool of human scorers to those who answered at least 100 questions (i.e., \variable{output/num_humans_with_more_than_100_scores.txt} humans). 
%The latter threshold was chosen to limit it to humans who seriously attempted to answer a part of the questions systematically. 
%This analysis might lead to potential biases, most likely in favor of humans, as they were allowed to skip questions. \variable{output/num_humans_with_204_scores.txt} humans answered more than 200 questions.
For the analysis, we treated each human as a model. We computed the topic aggregated averages per human for analyses grouped by topic and then averaged over all humans.

\subsection{Classification of questions into topics}\label{sec:meth-topic} 
% When curating our dataset, we systematically recorded keywords and sources.
% To allow for analysis of the model performance as a function of the topic, we leverage this information together with the output of sequence classification models.
% We use this information to make the assignment for questions that can easily be assigned to a topic based on the source (e.g., number of \gls{nmr} signals, chemical compatibility, toxicology exam questions).
% For the remaining ones, e.g., from chemistry olympiad questions, we use zero-short sequence classification\autocite{zeroshotsequence} using the BART model\autocite{bart, FacebookBART}, which our preliminary analysis found to be more robust than topic modeling based on embeddings from OpenAI's \texttt{ada} model or Cohere's \texttt{Cohembed-english-v3.0} model.

>>>>

% Importance of scale 
% Still lacks in knowledge-intensive questions

@@

\subsection{Model evaluation workflow}
An overview of the pipeline is shown in \Cref{fig:evaluation_workflow}.

@@

\paragraph{Parsing}
Our parsing workflow is multistep and primarily based on regular expressions.
In the case of instruction-tuned models, we first identify the \texttt{[ANSWER]}\texttt{[\textbackslash ANSWER]} environment we prompt the model to report the answer in.
In the case of completion models, this step is skipped. From there, we attempt to extract the relevant enumeration letters (for multiple-choice questions) or numbers.
In the case of numbers, our regular expression was engineered to deal with various forms of scientific notation.
As initial tests indicated that models sometimes return integers in the form of words, e.g., \enquote{one} instead of \enquote{1}, we also implemented a word-to-number conversion using regular expressions.
If these hard-coded parsing steps fail, we use a \gls{llm}, e.g., \ClaudeThreeFiveSonnet, to parse the completion.

\paragraph{Models}
For all models we performed inference using greedy decoding (i.e., temperature 0). We used the \gls{api} endpoints provided by the model developers and the ones provided by Groq.

@@

\paragraph{Comparison with models}
For the analysis, we treated each human as a model. We computed the topic aggregated averages per human for analyses grouped by topic and then averaged over all humans.

\subsection{Data annotation}\label{sec:meth-topic} 
% When curating our dataset, we systematically recorded keywords and sources.
% To allow for analysis of the model performance as a function of the topic, we leverage this information together with the output of sequence classification models.
% We use this information to make the assignment for questions that can easily be assigned to a topic based on the source (e.g., number of \gls{nmr} signals, chemical compatibility, toxicology exam questions).
% For the remaining ones, e.g., from chemistry olympiad questions, we use zero-short sequence classification\autocite{zeroshotsequence} using the BART model\autocite{bart, FacebookBART}, which our preliminary analysis found to be more robust than topic modeling based on embeddings from OpenAI's \texttt{ada} model or Cohere's \texttt{Cohembed-english-v3.0} model.
